%-------------------------------------------------------------------------------
% FIRST PAGE (EXECUTIVE SUMMARY)
%-------------------------------------------------------------------------------
{\begingroup
\setstretch{1.05} % compatta un po' rispetto al \onehalfspacing globale
%\vspace{-0.8em}

\makeatletter
\begingroup
\let\addcontentsline\@gobblethree
%-------------------------
\cvsection{Highlights}
%-------------------------

\textit{\small
My research develops \textbf{Stone-type categorical dualities} and representation theorems
linking the algebraic semantics of logic with topological structures.
I combine methods from universal algebra, topology and category theory to study structures arising from logic,
including MV-algebras, lattice-ordered groups, hyperdoctrines.
}




%\textit{\small
%I work at the interface of \stress{logic}, \stress{universal algebra}, \stress{topology} and \stress{category theory}.
%My research focuses on \stress{Stone-type categorical dualities} and representation theorems, with applications to various logics and their algebras (e.g.\ MV-algebras, lattice-ordered groups, hyperdoctrines).
%}

\vspace{0.6em}

% Two-column layout
\begin{minipage}[t]{0.48\textwidth}





%-------------------------
\cvsubsection{\stress{Selected publications}}
%-------------------------
\begin{itemize}
  \setlength\itemsep{0.25em}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Abbadini, Marra, Spada.
        {Stone--Gelfand duality for metrically complete lattice-ordered groups}.
        \textbf{\emph{Advances in Mathematics}} (2025).
  \item Abbadini, Di Liberti.
        {Duality for coalgebras for Vietoris and monadicity}.
        \textbf{\emph{The Journal of Symbolic Logic}} (2025).
  \item Abbadini, Aglian\`o, Fioravanti.
        {Varieties of MV-monoids and positive MV-algebras}.
        \textbf{\emph{Journal of Algebra}} (2025).
\end{itemize}

\vspace{1em}



%-------------------------
\cvsubsection{\stress{Major funding \& Projects}}
%-------------------------
\begin{itemize}
  \setlength\itemsep{0.25em}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item \textbf{Marie Sk{\l}odowska--Curie} Postdoctoral Fellowship (MSCA PF) (University of Birmingham, UK), 2023--2025.\\
        Project: \emph{DCPOS: Dualities via ComPactness, Openness and their Symmetry}.\\
        Supervisor: Achim Jung.
  \item \textbf{FSR Incoming} Postdoctoral Fellowship (Université catholique de Louvain, Belgium), 2025--2028.\\
        Project: \emph{CatCoD: Categorical Commutators and Dualities}.\\
        Supervisor: Marino Gran.
\end{itemize}

%%-------------------------
%\cvsubsection{\stress{Keywords}}
%%-------------------------
%\begin{itemize}
%  \setlength\itemsep{0.15em}
%  \setlength\parskip{0pt}
%  \setlength\parsep{0pt}
%  \item Duality \& representation theorems
%  \item Universal algebra; algebraic logic (MV-algebras, lattice-ordered groups)
%  \item Categorical logic
%  \item Topology \& coalgebraic methods in logic
%\end{itemize}

\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}


%\vspace{1em}


%-------------------------
\cvsubsection{\stress{Highlights}}
%-------------------------
\begin{itemize}
  \setlength\itemsep{0.25em}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item \stress{Publications:} 20 publications (18 journal articles, 1 book chapter, 1 proceedings paper). %, with venues such as \emph{Advances in Mathematics}, \emph{Journal of Symbolic Logic}, \emph{Journal of Algebra},  \emph{JPAA}, \emph{TAC}, etc.
  \item \stress{Invited talks:} invited plenary talks at international conferences, such as \emph{Topology, Algebra, and Categories in Logic 2026} %(Krak\'ow, Poland) 
  and \emph{BLAST 2023}. % (Charlotte, USA).
  \item \stress{Teaching:} teaching experience from first-year Bachelor's to Master’s level; currently teaching as a course holder for \emph{Categorical Dualities in Logic} (2025/26); Master’s thesis reader and co-supervision of BSc theses.
  \item \stress{Awards:} AILA Paolo Gentilini Prize (2026), AILA Ada Lettieri Prize (2025), and special mention for the AILA--UMI Franco Montagna Prize (2023).
%  \item \textbf{Teaching:} teaching experience from first-year Bachelor to Master’s level; current course holder for \emph{Categorical Dualities in Logic} (2025/26); co-supervision of BSc theses.
%  \item \textbf{Teaching:} experience as teaching assistant and adjunct professor; scheduled course holder (2025/26); co-supervision of BSc theses.
\item \stress{National qualifications:} Italian ASN (Seconda Fascia, 01/A1 Mathematical Logic, 2024); French MCF qualification (Mathematics \& Computer Science, 2023).
%  \item \stress{National qualifications:} Italian National Scientific Qualification (ASN, Seconda Fascia, 2024); French qualification as \emph{ma\^{\i}tre de conf\'erences} in Mathematics and Computer Science (2023).
\end{itemize}

\end{minipage}

\vspace{1em}
{\small\color{lighttext}Full publication list, talks, teaching and service appear in the following pages.}


 \endgroup
 \makeatother

\endgroup}
