%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Talks}


\newcounter{talkscounter}
\newcommand\increaseandshowtalks{\addtocounter{talkscounter}{1}\thetalkscounter}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\vspace{-0.3cm}
%\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}


%-------------------------------------------------------------------------------
\cvsubsection{\stress{Invited plenary talks at international conferences}}
%-------------------------------------------------------------------------------


\begin{cvpubs}

	\cvpub{
		\increaseandshowtalks. {\href{https://iphils.uj.edu.pl/tacl/}{Topology, Algebra, and Categories in Logic}}. {\gray Kraków (Poland). (2026.07.27 -- 2026.07.31)}\\
		\textit{TBA}.
	}

	\cvpub{
		\increaseandshowtalks. {\href{https://pages.charlotte.edu/blast2023/}{Boolean Algebras, Lattices, Universal Algebra, Set Theory, Topology}}. {\gray University of North Carolina at Charlotte (USA). (2023.05.17)}\\
		\textit{Positive MV-algebras}.
	}

\end{cvpubs}

\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Invited talks at special/thematic sessions in international conferences}}
%-------------------------------------------------------------------------------

\begin{cvpubs}

	\cvpub{
		\increaseandshowtalks.
		{\href{https://sites.google.com/fct.unl.pt/tca2026/}{Conference on Theoretical and Computational Algebra 2026}}. {\gray University of Minho, Guimarães (Portugal). Invited to the Thematic Session on Duality theory. (2026.06.29)}\\
		\textit{Adding quantifiers via Stone duality}.
	}
	% Abstract:
	% Herbrand's theorem, in its weak form, describes provability of an existential formula in terms of the provability of suitable quantifier-free formulas. I will present a Stone-dual perspective on this result. In particular, I will explain how the Stone spaces of pointed models of a universal theory, identified according to the existential formulas they satisfy, can be reconstructed from the corresponding spaces obtained using only quantifier-free formulas.
	% The motivation comes from the search for explicit Stone-dual descriptions of free algebras and colimits in first-order logic. In the propositional setting, such descriptions are comparatively direct, and they underlie short dual proofs of results such as interpolation and Beth definability. In the first-order setting, by contrast, quantifiers make the picture substantially more delicate. This suggests a step-by-step approach, in which quantifiers are added one layer at a time. From this perspective, the Stone dual of Herbrand's theorem can be seen as a first step in the process of adding quantifiers via Stone duality.

	\cvpub{
		\increaseandshowtalks.
		{\href{https://asl2024.sites.iastate.edu/}{Association for Symbolic Logic North American Annual Meeting}}. {\gray Iowa State University (USA). Invited to the Special Session on Algebraic Logic. (2024.05.15)}\\
\textit{A duality for metrically complete lattice-ordered groups}.
	}

\end{cvpubs}

\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Invited talks at international workshops}}
%-------------------------------------------------------------------------------

\begin{cvpubs}

	\cvpub{
		\increaseandshowtalks. {\href{https://sites.google.com/view/tolo7/}{International Workshop on Topological Methods in Logic}}. {\gray Ivane Javakhishvili State University (Georgia). (2025.06.25)}\\
		\textit{The unification type of {\L}ukasiewicz logic with a bounded number of variables}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://algebraweeksiena.wordpress.com/}{Third Algebra Week (2023)}}. {\gray University of Siena (Italy). (2023.07.05)}\\
		\textit{Positive subreducts of MV-algebras}.
	}

  \cvpub{
  	\increaseandshowtalks. {\href{http://logica.dipmat.unisa.it/DOCToR/index.html}{Duality, Order, (Co)algebras, Topology and Related topics}}. {\gray Online. (2021.07.07)}\\ % (Workshop in the occasion of the Ph.D.\ graduation of M.\ Abbadini and L.\ Carai)
 	  \textit{Unital commutative distributive $\ell$-monoids and their unit intervals}. 
  }

   \cvpub{
   	\increaseandshowtalks. {\href{https://algebraweeksiena.wordpress.com/}{Third Algebra Week (2020)}}. {\gray University of Siena (Italy). (2020.05) (Cancelled due to COVID-19 pandemic.)}\\
  		\textit{Equivalence à la Mundici for lattice-ordered monoids}. 
   }

\end{cvpubs}



\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Invited talks at national conferences}}
%-------------------------------------------------------------------------------

\begin{cvpubs}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://aila2026.github.io/}{Meeting of the Italian Association of Logic and its Applications}}. {\gray Rome (Italy). (2026.09.14 -- 2026.09.18)}\\
		\textit{TBA}.
	}
\end{cvpubs}


%-------------------------------------------------------------------------------
\cvsubsection{\stress{Invited talks at national workshops}}
%-------------------------------------------------------------------------------

\begin{cvpubs}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://www.anupamdas.com/smls4/}{Southern and Midlands Logic Seminar}}. {\gray University of Birmingham (UK). (2023.12.13)}\\
		\textit{Natural dualities}.
	}
\end{cvpubs}


\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Invited talks at local workshops}}
%-------------------------------------------------------------------------------

\begin{cvpubs}

	\cvpub{
			\increaseandshowtalks. {Workshop on Categorical-Algebraic Structures}. {\gray Stellenbosch University (South Africa). (2026.04.30)}\\
		\textit{Ideals and slices over the initial algebra}.
	}

\end{cvpubs}



\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Contributed talks at international peer-reviewed conferences}}
%-------------------------------------------------------------------------------



\begin{cvpubs}
\cvpub{
	\increaseandshowtalks. {\href{https://sites.google.com/view/pssl112/}{Peripatetic Seminar on Sheaves and Logic}}. {\gray University of Nottingham (UK). (2026.03.29)}\\
	\textit{The doctrinal Herbrand’s theorem and its Stone dual}.
}
	
		\cvpub{
		\increaseandshowtalks. {\href{https://progetto-itaca.github.io/ItaCa-25/}{ItaCa Workshop}}. {\gray University of Milan (Italy). (2025.12.22)}\\
		\textit{The doctrinal Herbrand's theorem and its Stone dual}.
	}


	\cvpub{
		\increaseandshowtalks. {\href{https://sites.google.com/view/aalogic/aal-conference-2025}{Australasian Association for Logic Conference}}. {\gray University of Queensland (Australia, online). (2025.11.03)}\\
		\textit{Natural duality for finitely valued algebras}.
	}


	\cvpub{
		\increaseandshowtalks. {\href{https://richardblute.ca/octoberfest-2025/}{Category Theory Octoberfest}}.
		{\gray Online. (2025.10.25)}\\
		\textit{On the category of metric compact Hausdorff spaces}.
	}



	\cvpub{
		\increaseandshowtalks. {\href{https://www.congressi.unisi.it/latd25/}{Logic, Algebra and Truth Degrees}}.
		{\gray University of Siena (Italy). (2025.07.25)}\\
		\textit{The algebraic structure of spaces of integrable functions}.
	}
	
	
	\cvpub{
		\increaseandshowtalks. {\href{https://www.colloquium.co/lc2025}{Logic Colloquium}.}
		{\gray TU Wien (Austria). (2025.07.07)}\\
		\textit{An algebraic version of Herbrand’s theorem}.
	}

	\cvpub{
		\increaseandshowtalks. {\href{https://www.bfh.ch/en/news/events-for-specialists/aaa107/}{Workshop on General Algebra}}.
		{\gray Bern (Switzerland). (2025.06.21)}\\
		\textit{The algebraic structure of spaces of integrable functions}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://www.ioc.ee/~amar/pssl110/}{Peripatetic Seminar on Sheaves and Logic}}.
		{\gray Tallinn University of Technology (Estonia). (2025.05.03)}\\
		\textit{Barr-coexactness of metric compact Hausdorff spaces}.
	}

	\cvpub{
		\increaseandshowtalks. {\href{https://www.mat.uc.pt/~sumtopo/}{Summer Conference on Topology and its Applications}}.
		{\gray University of Coimbra (Portugal). (2024.07.09)}\\
			\textit{Vietoris endofunctor for closed relations and its de Vries dual}.
	}

	\cvpub{
		\increaseandshowtalks. {\href{https://iiia.csic.es/tacl2024/}{Topology, Algebra, and Categories in Logic}}.
		{\gray University of Barcelona (Spain). (2024.07.04)}\\
		\textit{Vietoris endofunctor for closed relations and its de Vries dual}.
	}

	
	\cvpub{
		\increaseandshowtalks. {\href{https://aaa104.swu.bg/aaa104-2023/cfp}{Workshop on General Algebra}}. {\gray South-West University ``Neofit Rilsk'' (Bulgaria). (2024.02.10)}\\
		\textit{Natural dualities with an infinite dualizing object}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://sites.google.com/view/mosaic2023/}{Modalities in Substructural Logics: Theory, Methods and Applications}}. {\gray Vienna (Austria). (2023.09.29)}\\
		\textit{Stone duality for finitely valued algebras with a near-unanimity term}.
	}

	\cvpub{
		\increaseandshowtalks. {\href{https://sites.google.com/view/beppemetere/pssl-108}{Peripatetic Seminar on Sheaves and Logic}}. {\gray University of Palermo (Italy). (2023.09.17)}\\
		\textit{Soft sheaf representations in Barr-exact categories}.
	}

	\cvpub{
		\increaseandshowtalks. {\href{https://sites.google.com/view/latd-2023/}{Logic, Algebra and Truth Degrees}}. {\gray Ivane Javakhishvili State University (Georgia). (2023.09.11)}\\
		\textit{Free extensions}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://lc2023.unimi.it/}{Logic Colloquium}}.
		{\gray University of Milan (Italy). (2023.06.08)}\\
		\textit{J\'onsson-Tarski duality beyond dimension 0}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://progetto-itaca.github.io/ItaCa-22/}{ItaCa Workshop}}. {\gray University of Pisa (Italy). (2022.12.21)}\\
		\textit{Comonadicity over $\mathsf{Set}$ of coalgebras of Vietoris functors}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://www.mat.uc.pt/~tacl2022/}{Topology, Algebra and Categories in Logic}}. {\gray University of Coimbra (Portugal). (2022.06.24)}\\
		\textit{An approach à la de Vries for compact Hausdorff spaces and closed relations}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://sites.google.com/view/ct2021/}{Category Theory}}. {\gray University of Genoa (Italy). (2021.09.01)}\\
		\textit{The opposite of the category of compact ordered
			spaces is monadic over the category of sets}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://math.nmsu.edu/blast-2021/}{Boolean Algebras, Lattices, Universal Algebra, Set Theory, Topology}}. {\gray New Mexico State University (USA, online). (2021.06.13)}\\
		\textit{The opposite of the category of compact ordered spaces as an infinitary variety}.
	}
	
	\cvpub{
		\increaseandshowtalks. {Workshop on General Algebra}. {\gray University of Siena (Italy). (2020.02.21)}\\
		\textit{Priestley duality above dimension zero: algebraic axiomatisability of the dual of compact ordered spaces}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://math.univ-cotedazur.fr/tacl/2019/}{Topology, Algebra, and Categories in Logic}}. {\gray University of Nice (France). (2019.06.20)}\\
		\textit{Norm-complete Abelian $\ell$-groups: equational axiomatization}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://mathsites.unibe.ch/phdlogic2019/}{PhDs in Logic}}. {\gray University of Bern (Switzerland). (2019.04.25)}\\
		\textit{Stone-Gelfand duality for groups}.
	}
	
	\cvpub{
		\increaseandshowtalks. {Boolean Algebras, Lattices, Universal Algebra, Set Theory, Topology}. {\gray University of Denver (USA). (2018.08.10)}\\
		\textit{Operations that preserve integrability, and truncated Riesz spaces}.
	}
	
\end{cvpubs}


\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Contributed talks at national peer-reviewed conferences}}
%-------------------------------------------------------------------------------




	\cvpub{
		\increaseandshowtalks. {\href{https://ailameeting24.uniud.it/}{Meeting of the Italian Association of Logic and its Applications}}. {\gray University of Udine (Italy). (2024.09.04)}\\
		\textit{Vietoris endofunctor for closed relations and its de Vries dual}.
	}

\cvpub{
		\increaseandshowtalks. {\href{https://www.ailalogica.it/incontro2022/}{Meeting of the Italian Association of Logic and its Applications}}. {\gray Vanvitelli University (Italy). (2023.09.13)}\\
	\textit{Duality for metrically complete Abelian $\ell$-groups}.
}


\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Talks at local seminars}}
%-------------------------------------------------------------------------------


\begin{cvpubs}

	\cvpub{
		\increaseandshowtalks. {University of KwaZulu-Natal} (Durban, South Africa). {\gray (2026.05.21)}\\
		\textit{On the symmetry between openness and compactness}.
	}
	% Abstract:
	% In my area of research, namely Stone dualities and their generalizations, one works with topological spaces that display a remarkable symmetry between open sets and compact saturated sets. For the purposes of this talk, you may simply think of compact saturated sets as compact sets: in Hausdorff spaces the two notions coincide. In some important classes of spaces, such as Stone spaces, spectral spaces, and stably compact spaces, this symmetry is complete. In others, most notably sober spaces, it is not complete, but it is still very strong.
	% Partly motivated by the appeal of symmetry itself, and partly by the practical advantage that symmetry can let us prove two results for the price of one, I investigated a mild generalization of topological spaces in which open sets and compact saturated sets enjoy a fully formal symmetry. In this setting, once one proves a statement involving opens and compact saturated sets, one automatically gets a dual statement by exchanging the two notions.
	% My interest in these objects comes from the fact that they still admit a categorical duality, generalizing the classical duality between sober spaces and spatial frames, but now in a context where openness and compactness are placed on completely equal footing.
	% In its full generality, this comes at a price: one has to take both notions, open and compact saturated, as primitive.
	% In the talk I will explain these ideas.

	\cvpub{
		\increaseandshowtalks. {Université catholique de Louvain} (Belgium). %Junior Colloquium. 
		{\gray (2025.10.29)}\\
		\textit{Bridging Ordered Groups and Topology: Representation Theorems and Categorical Dualities}.
	}

	\cvpub{
		\increaseandshowtalks. {University of Birmingham} (UK). {\gray (2025.06.05)}\\
		\textit{On de Groot and Lawson self-dualities}.
	}

	\cvpub{
		\increaseandshowtalks. {University of Birmingham} (UK). {\gray (2025.05.08)}\\
		\textit{Freely adding a layer of Heyting implication to a distributive lattice}.
	}

	\cvpub{
		\increaseandshowtalks. {University of Salerno} (Italy). {\gray (2025.04.24)}\\
		\textit{An algebraic version of Herbrand’s theorem}.
	}

	\cvpub{
		\increaseandshowtalks. {Université catholique de Louvain} %, Louvain-la-Neuve, 
		(Belgium). %Category Theory Seminar. 
		{\gray (2025.01.07)}\\
		\textit{Coalgebraic flavour of metric compact Hausdorff spaces}.
	}

	\cvpub{
		\increaseandshowtalks. {University of Milan} (Italy). % Logic, Algebra and Categories. 
		{\gray (2024.10.31)}\\
		\textit{Quantifier-free fragments and quantifier alternation depth in doctrines}.
	}


	\cvpub{
		\increaseandshowtalks. {University of Manchester} (UK). {\gray (2024.10.09)}\\
		\textit{Quantifier-free fragments and quantifier alternation depth in doctrines}.
	}

	\cvpub{
		\increaseandshowtalks. {University of Padua} (Italy). {\gray(2024.05.02)}\\
		\textit{Quantifier alternation depth in universal Boolean doctrines}.
	}
	
	\cvpub{
		\increaseandshowtalks. {University of Birmingham} (UK). {\gray (2023.11.23)}\\
		\textit{An abstraction of the unit interval with Euclidean topology and denominators}.
	}
	
	\cvpub{
		\increaseandshowtalks. {Université catholique de Louvain} %, Louvain-la-Neuve, 
		(Belgium). %Category Theory Seminar. 
		{\gray (2023.11.13)}\\
		\textit{Soft sheaf representations in Barr-exact categories}.
	}
	
	\cvpub{
		\increaseandshowtalks. {University of Bern} (Switzerland). %Bern Logic Seminar. 
		{\gray (2023.04.20)}\\
		\textit{Positive MV-algebras}.
	}

	\cvpub{
		\increaseandshowtalks. {University of the Witwatersrand} %Johannesburg, 
		(South Africa). {\gray (2023.03.30)}\\
		\textit{Unique embeddability property}.
	}	
	
	\cvpub{
		\increaseandshowtalks. {Paris-Saclay University} %Laboratoire Méthodes Formelles (LMF), Paris, 
		(France, online). {\gray (2023.01.04)}\\
		\textit{An abstraction of the unit interval with denominators}.
	}
	
	\cvpub{
		\increaseandshowtalks. {University of Padua} (Italy, online). {\gray (2022.12.05)}\\
		\textit{Dualities for compact Hausdorff spaces}.
	}
	
	\cvpub{
		\increaseandshowtalks. {Université Paris Cité}
		 %IRIF, 
		 (France). %Sémantique. 
		 {\gray (2022.11.25)}\\
		\textit{A generalization of de Vries duality to closed relations between compact Hausdorff spaces}.
	}
	
	\cvpub{
		\increaseandshowtalks. {University of Amsterdam}
		(Netherlands). % Institute for Logic, Language and Computation, Netherlands, online. Lectures on Logic and its Mathematical Aspects (LLAMA seminar). 
		{\gray (2022.05.11)}\\
			\textit{A generalization of de Vries duality to closed relations between compact Hausdorff spaces}.
	}

	\cvpub{
		\increaseandshowtalks. {New Mexico State University} (USA, online). %Algebra Seminar. 
		(2022.03.14)\\
		\textit{Free extension for universal algebras}.
	}

	\cvpub{
		\increaseandshowtalks. {University of Caserta} (Italy). %Model theory seminar. 
		{\gray (2022.02.14)}\\
		\textit{Positive MV-algebras}.
	}

	\cvpub{
		\increaseandshowtalks. {University of Denver} (USA, online). %Nonclassical Logic Webinar. 
		{\gray (2021.05.05)}\\
		\textit{Is the category of locally finite MV-algebras equivalent to an equational class?}
	}
		
	\cvpub{
		\increaseandshowtalks. {University of Denver} (USA, online). %Nonclassical Logic Seminar. 
		{\gray (2020.05.08)}\\
		\textit{Equivalence à la Mundici for lattice-ordered monoids}.
	}
  	
	\cvpub{
		\increaseandshowtalks. {University of Salerno} (Italy). {\gray  (2020.01.23)}\\
		\textit{Equivalence \`a la Mundici for lattice-ordered monoids}.
	}
	
	\cvpub{
 		\increaseandshowtalks. {University of Nice} (France). %Groupe de travail `Dualité de Stone, langages formels et logique'. 
		{\gray (2019.10.03)}\\
% 		Laboratoire Math\'ematiques J.\ A.\ Dieudonné, 
 		\textit{On concrete dual adjunctions}.
 	}

	\cvpub{
		\increaseandshowtalks. {Czech Academy of Sciences} %Prague, 
		(Czech Republic). %Applied Mathematical Logic Seminar. 
		{\gray (2019.02.06)}\\
%		Institute of Computer Science,
		\textit{The dual of compact ordered spaces is a variety}.
	}
		
	\cvpub{
		\increaseandshowtalks. {University of Salerno} (Italy). {\gray (2018.12.13)}\\
		\textit{Archimedean Cauchy-complete MV-algebras form a variety}.
	}

		
	\cvpub{
		\increaseandshowtalks. {University of Milan} (Italy). %Workshop ``PhD\^{}2 - PhD days''. 
		{\gray (2018.07.06)}\\
		\textit{Operations that preserve integrability: characterization and related algebraic structures}.
	}
  		
\end{cvpubs}


\medskip

%-------------------------------------------------------------------------------
\cvsubsection{\stress{Other talks and posters}}
%-------------------------------------------------------------------------------


	
\begin{cvpubs}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://www.mathematik.uni-muenchen.de/~schwicht/pc24.php}{Autumn school ``Proof and Computation''}}, Fischbachau (Germany). 
		5-minute lightning talk.
		{\gray (2024.09.19)}\\
		\textit{Algebras of logic, step-by-step}.
	}
	
	\cvpub{
		\increaseandshowtalks. {\href{https://umi.dm.unibo.it/congresso2019/}{Congresso dell'Unione Matematica Italiana}}, University of Pavia (Italy). 
		Poster.
		(2019.09.02)\\
		\textit{Dualità di Stone-Gelfand per i gruppi}.
	}

\end{cvpubs}
